\ProcessOptions\relax
\documentclass[9pt, legalpaper]{article}  
\usepackage[english]{babel}
\usepackage{titlesec}
\usepackage{xcolor}

% Set document margins
\usepackage[left=0.75in,top=0.5in,right=0.75in,bottom=0.5in]{geometry}

\usepackage[familydefault,light]{Chivo}

% Set font face
\usepackage{fontspec}
\setmainfont[SmallCapsFeatures={Renderer=Basic},
Ligatures={TeX, NoCommon, NoDiscretionary}]{Chivo}

\usepackage[parfill]{parskip}

% Required for ifthenelse statements
\usepackage{etoolbox} 

% No Page numbers
\pagestyle{empty}

% Flexible Tables
\usepackage{tabu}

% For custom margins
\usepackage{changepage}

% To customize lists
\usepackage{enumitem}
\setlist{leftmargin=*, noitemsep, topsep=-1\parskip}

% For microtype
\usepackage{microtype}

\usepackage{amssymb}

% Hyperlinks
\usepackage{hyperref}
\hypersetup{
	colorlinks=true,
	linkcolor=black,
	urlcolor=darkgray,
	pdftitle={Joseph Alcantara CV},
}

\titleformat{\section}
{\normalfont\Large\bfseries}{\thesection}{1em}{}[{\titlerule[0.8pt]}]

%--------------------------------------------------------------------------------
%                                    Constants                                  -
%--------------------------------------------------------------------------------
\def\afterheaderspace{1pt}
\def\beforesectionheaderspace{4pt}
\def\sectionheadermargin{6pt}
\def\aftersectionheaderspace{-4pt}
\def\sectionheaderhrlueheight{0.5pt}
\def\aftersinglelinesubsectionheaderspace{-18.5pt}
\def\afterdoublelinesubsectionheaderspace{-10pt}
\def\aftermultilinesubsectionheaderspace{-6pt}
\def\afteremptysubsectionheaderspace{1pt}
\def\subsectionmargin{9pt}
\def\aftersubsectionspace{2pt}

%--------------------------------------------------------------------------------
%                            Header Setup and Printing                          -
%--------------------------------------------------------------------------------
\makeatletter

\newcommand\address[1]{\def\@address{#1}}
\address{}

\newcommand\printaddress{
	\scriptsize{\@address}
}

\newcommand\name[1]{\def\@name{#1}}
\name{}

\newcommand\printname{
	\textbf{\Large\textsc{\@name}}
}

\newcommand\contacts[1]{\def\@contacts{#1}}
\contacts{}

\newcommand\printcontacts{
	\scriptsize{\@contacts}
}

\newcommand\makeheader{
	\begin{center}
		\begin{tabu} to 1\textwidth { X[1,l,m] X[2,c,m] X[1.3,r,m] }
			\printaddress & \printname & \printcontacts \\
		\end{tabu}	
	\end{center}
	\vspace*{\afterheaderspace}
}
\makeatother

%--------------------------------------------------------------------------------
%                            Sections and Subsections                           -
%--------------------------------------------------------------------------------
\makeatletter
\newenvironment{cvsection}[1]{
	\vspace*{\beforesectionheaderspace}
	\begin{adjustwidth}{\sectionheadermargin}{\sectionheadermargin}
		\textsc{\textbf{#1}}
	\end{adjustwidth}
	\smallskip
	\hrule height \sectionheaderhrlueheight
	\vspace*{\aftersectionheaderspace}
}{}
\makeatother

\makeatletter
\newtoggle{lefttitledefined}
\newtoggle{centertitledefined}
\newtoggle{righttitledefined}

\newenvironment{cvsubsection}[4][1]{
	\notblank{#2}{\toggletrue{lefttitledefined}}{}
	\notblank{#3}{\toggletrue{centertitledefined}}{}
	\notblank{#4}{\toggletrue{righttitledefined}}{}
	\ifboolexpr{togl {lefttitledefined} or togl {centertitledefined} or togl {righttitledefined}}{
		\begin{tabu} to 1\textwidth { X[l,p] X[c,p] X[r,p] }
			\textbf{#2} & \textbf{#3} & \textbf{#4} \\
		\end{tabu}
		\ifnumcomp{#1}{=}{1}{\vspace*{\aftersinglelinesubsectionheaderspace}}{
			\ifnumcomp{#1}{=}{2}{\vspace*{\afterdoublelinesubsectionheaderspace}}{
				\vspace*{\aftermultilinesubsectionheaderspace}
			}
		}
	}{
		\vspace*{\afteremptysubsectionheaderspace}
	}
	\togglefalse{lefttitledefined}
	\togglefalse{centertitledefined}
	\togglefalse{righttitledefined}
	\begin{adjustwidth}{\subsectionmargin}{\subsectionmargin}
	}
	{
	\end{adjustwidth}
	\vspace*{\aftersubsectionspace}
}
\makeatother

%================================================================================
%                              APPLICANT'S DATA                                 =
%================================================================================

\name{Joseph Alcantara}
\address{Dumaguete City, Philippines \linebreak \href{https://www.github.com/josephnicholas}{github.com/josephnicholas}}
\contacts{(+63) 919-846-6985 \linebreak joseph.nicholas.r.alcantara@gmail.com}

\begin{document}
	\makeheader
	
	%--------------------------------------------------------------------------------
	%                            PROFESSIONAL SUMMARY                               -
	%--------------------------------------------------------------------------------
	\begin{cvsection}{Professional Summary}
		\begin{cvsubsection}{}{}{}
			\color{darkgray}
			Software Engineer with 10+ years of experience building low-latency financial systems, from cryptocurrency matching engines and FIX protocol implementations to distributed post-trade platforms on AWS. Led a team of engineers developing a matching engine for a regulated digital asset exchange, and currently designs event-driven architectures using DynamoDB Streams, Lambda, SQS, and Redis for real-time notification delivery in trading systems. Deep C++ experience spanning codebase modernization (C++98 to C++20), performance profiling with Valgrind and uftrace, and Unix socket-level performance benchmarking.
		\end{cvsubsection}
	\end{cvsection}
	
	%--------------------------------------------------------------------------------
	%                            EMPLOYMENT HISTORY                                 -
	%--------------------------------------------------------------------------------
	\begin{cvsection}{Employment History}
		
		%--- IRESS ---
		\begin{cvsubsection}{Software Engineer}{Iress, Philippines}{June 2023 -- Present}
			\color{darkgray}
			\begin{itemize}
				\item Designed and implemented an event-driven permission notification system using DynamoDB Streams, Lambda, SQS, and Redis Pub/Sub, delivering real-time permission change events to multiple BFF pods via Server-Sent Events (SSE). Used DynamoDB Streams as the single source of truth to eliminate dual-write risks.
				\item Identified and resolved an out-of-order message delivery problem in the permission event pipeline caused by partial SQS batch failures during Lambda retries. Implemented version-based idempotency using DynamoDB Stream sequence numbers, allowing consumers to discard stale updates.
				\item Implemented centralized cache invalidation across multiple BFF pods using FusionCache with Redis ElastiCache as the distributed L2 cache and Redis Pub/Sub backplane.
				\item Developed backend services for the post-trade allocation system using the BFF pattern with ASP.NET Core, providing position summary and account details to fund managers for trade allocation workflows.
				\item Identified a race condition in the Trade Summary SSE streaming service where parallel firm snapshot loading set a completion flag prematurely, causing inconsistent data. Proposed fix adopted by the team.
				\item Developed a performance testing framework for InteropIO (Glue42) post-trade widgets using Playwright with Chrome DevTools Protocol, measuring render time, memory usage, and script execution.
				\item Led the 64-bit migration of a legacy C++ trading platform, upgrading from C++98 to C++20. Built Python tooling to automate symbol extraction from linker error logs and validate exports for duplicates.
				\item Built proof-of-concept post-trade widgets using React, ag-grid, and InteropIO (Glue42) to validate cross-widget communication patterns for the next-generation trading UI.
			\end{itemize}
		\end{cvsubsection}
		
		%--- ARCHAX ---
		\begin{cvsubsection}{Software Engineer}{Archax, Philippines}{February 2021 -- June 2023}
			\color{darkgray}
			\begin{itemize}
				\item Led a team of 3 engineers developing and maintaining the matching engine for Archax, a regulated digital securities exchange.
				\item Built a performance benchmarking tool that sends order message payloads over \textit{Unix sockets} and calculates throughput and latency metrics, used to establish baselines and detect regressions.
				\item Implemented round-robin connection/reconnection logic with configurable timeout intervals and non-blocking connect for matching engine client sessions.
				\item Implemented message version validation on client login, detecting protocol mismatches before order flow begins and preventing silent message corruption.
				\item Designed the OMS load balancing architecture for multi-organization support, including a metric collection service for organization-to-OMS rebalancing with scheduled and admin-triggered modes.
				\item Designed and implemented a subscription model for the OMS, enabling each instance to selectively process only inbound matching engine messages for its subscribed organizations---a prerequisite for horizontal scaling.
				\item Designed and implemented risk limit management for the OMS, including configurable controls for single-order and daily-aggregate limits.
				\item Designed and deployed a FIX protocol test client in \textit{Golang} using QuickFIX, supporting standard message validation and burst mode for benchmarking the FIX middleware.
				\item Initiated CPU profiling of the OMS using \textit{uftrace} and \textit{Callgrind} to identify hot paths, leading to targeted optimizations in the order processing pipeline.
			\end{itemize}
		\end{cvsubsection}
		
		%--- CRYPTOBLK ---
		\begin{cvsubsection}{Senior Engineer}{CryptoBLK, Hong Kong}{March 2019 -- March 2021}
			\color{darkgray}
			\begin{itemize}
				\item Integrated the Dilithium post-quantum signature scheme into the Abelian cryptocurrency, replacing select ed25519 computations with lattice-based cryptography for quantum-resistant keys and signatures.
				\item Integrated quantum-proof linkable ring signatures (\textit{SALRS}) into the Abelian project, advancing post-quantum privacy guarantees.
				\item Implemented a Solidity ERC-20 token smart contract for the Abelian (ABE) ICO on Ethereum.
				\item Designed and implemented integration tests, Corda flow tests, and contract tests for the Letter of Credit amendment feature on the Contour trade finance platform. Built the corresponding Corda smart contracts and Spring API endpoints.
			\end{itemize}
		\end{cvsubsection}
		
		%--- RETONE ---
		\begin{cvsubsection}{Software Engineer}{Retone, Remote}{July 2020 -- February 2021}
			\color{darkgray}
			\begin{itemize}
				\item Implemented sharding for concurrent magnetic field computations in the Radia engine, parallelizing previously sequential workloads. Developed a software-based UART reader/writer for microcontroller pre-deployment validation.
			\end{itemize}
		\end{cvsubsection}
		
		%--- LEXMARK ---
		\begin{cvsubsection}{Firmware Engineer}{Lexmark, Philippines}{November 2018 -- March 2019}
			\color{darkgray}
			\begin{itemize}
				\item Implemented Apple SMTP handling for legacy printers (\textit{Embedded C++}). Migrated build system from Unix Makefiles to \textit{CMake}. Resolved 30+ firmware defects identified by Coverity and SonarQube.
			\end{itemize}
		\end{cvsubsection}
		
		%--- FIRO & HORIZEN ---
		\begin{cvsubsection}{Freelance Software Engineer}{Firo \& Horizen, Remote}{January 2018 -- September 2018}
			\color{darkgray}
			\begin{itemize}
				\item Deployed CI/CD pipelines (Travis CI, CircleCI, Jenkins, gitian-builder) producing reproducible builds across 3 platforms. Integrated the MTP protocol upgrade into the ElectrumX wallet server. \textit{(Firo)}
				\item Integrated Horizen cryptocurrency into the Ledger Nano S hardware wallet. Implemented domain fronting for the Horizen light wallet to bypass network restrictions. \textit{(Horizen)}
			\end{itemize}
		\end{cvsubsection}
		
		%--- NCR ---
		\clearpage
		\begin{cvsubsection}{Software Engineer}{NCR Corporation, Philippines}{August 2012 -- February 2018}
			\color{darkgray}
			\begin{itemize}
				\item Integrated payment terminals (AMEX) and third-party hardware (scales, IBM POS) into NCR self-service checkout systems across deployments including Australia Post, Walmart, and Post Office UK. Primarily MFC C++.
				\item Built diagnostic tooling (C\# log parser with telnet, predictive test scripts) for IBM POS and configured Jenkins CI for automated nightly builds.
			\end{itemize}
		\end{cvsubsection}
		
	\end{cvsection}
	
	%--------------------------------------------------------------------------------
	%                                 EDUCATION                                     -
	%--------------------------------------------------------------------------------
	\begin{cvsection}{Education}
		\begin{cvsubsection}{Dumaguete City, Philippines}{Silliman University}{March 2012}
			\color{darkgray}
			\begin{itemize}
				\item B.S in Computer Engineering. Thesis: Android-controlled quadrotor with Bluetooth communication.
			\end{itemize}
		\end{cvsubsection}
		\begin{cvsubsection}{Remote}{ConsenSys Academy}{October 2019}
			\color{darkgray}
			\begin{itemize}
				\item Ethereum Developer Bootcamp. Project: \href{https://github.com/josephnicholas/proposal-dapp}{Proposal DApp}
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	%--------------------------------------------------------------------------------
	%                             TECHNICAL SKILLS                                  -
	%--------------------------------------------------------------------------------
	\begin{cvsection}{Technical Skills}
		\color{darkgray}
		\begin{cvsubsection}{}{}{}
			\textbf{Languages:} C++ (98/11/14/17/20), C\#/.NET 8, Python, Golang, TypeScript, JavaScript, Solidity, SQL
			
			\textbf{Cloud \& Infrastructure:} AWS (Lambda, DynamoDB, DynamoDB Streams, SQS, SNS, EventBridge, ElastiCache Redis, EKS, CloudWatch, IAM), Terraform, Docker, Kubernetes
			
			\textbf{Trading \& Financial:} FIX Protocol (OnixS SDK, QuickFIX), Matching Engine development, OMS, Post-trade allocation, Risk management
			
			\textbf{Frameworks:} ASP.NET Core, React, Node.js, Corda, Spring, Boost, Abseil, ZeroMQ, Protobuf, FlatBuffers
			
			\textbf{Data \& Messaging:} DynamoDB, PostgreSQL, SQLite, Redis (caching + Pub/Sub), FusionCache, Server-Sent Events
			
			\textbf{Performance \& Testing:} Valgrind, Callgrind, KCachegrind, uftrace, gprof, Grafana k6, Playwright + CDP, Datadog, Catch2, Google Test, xUnit
			
			\textbf{Tools:} Git, CMake, Bazel, Docker, Vim, JetBrains IDEs, Visual Studio, TeamCity, Conan, gdb, Sanitizers
		\end{cvsubsection}
	\end{cvsection}
	
\end{document}